\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2018-11-22 write_up/mixfishsim_ecolmod.tex
Bug fix for annual closures
Revised plot
Text update

\replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} spatially
and temporally heterogeneous fish populations, using species-unselective gear
that can result in unintended, unwanted catch of low quota or protected
species. Reducing these unwanted catches is crucial for biological and economic
sustainability of `mixed fisheries' and implementation of an ecosystem approach
to fishing. \\

\replaced[id = PD]{If fisheries are to avoid unwanted catch}{To implement
	effective spatial measures to reduce discards} a good understanding of
spatiotemporal fishery dynamics is required. However, traditional scientific
advice is limited by a lack of highly resolved knowledge of population
distribution, movement and how fishers interact with different fish
populations. This reflects that data on fish location at high temporal and
spatial resolutions is expensive and difficult to collect and therefore proxies
inferred from either scientific surveys or commercial catch data are often used
to model distributions, often with limited spatial and temporal resolution. \\

To understand how resolution impacts mixed fisheries inference, we develop a
highly resolved spatiotemporal simulation model incorporating: i)
delay-difference population dynamics, ii) population movement using Gaussian
Random Fields to simulate patchy, heterogeneously distributed populations, and
iii) fishery dynamics for multiple fleet characteristics based on targeting
via correlated random walk movement and learned behaviour. \\

We simulate 20 years of exploitation of the fish populations and use the
results from the fishing model to draw inference on the underlying population
structures. We compare this inference to i) a simulated fixed-site sampling
design commonly used for fisheries monitoring purposes, and ii) the true
underlying population structures input to the simulation, to establish the
potential and limitations of fishery-dependent data - an inherently biased
sampling method due to fisher's targeting- to provide a robust picture of
spatiotemporal distributions. Finally, we simulate an area closure based on
areas defined from commercial the known ("real-population") distribution,
commercial catch data and survey data at different temporal and spatial
resolutions and assess their effectiveness on reducing catches of a fish
population. \\

@@

Fishers exploit fish populations that are heterogeneously distributed in space
and time with varying knowledge of species distributions using
species-unselective fishing gear. \added[id=PD]{In doing so} fisheries
\deleted[id=PD]{that} catch an assemblage of species
\added[id=PD]{and}\deleted{, known as mixed fisheries} \replaced[id=JJ]{may}{,
	when managed by single-species quotas can end up}
discard\deleted[id=JJ]{ing} overquota catch \added[id=JJ]{when managed by
	single species quotas,} leading to overexploitation of fish populations
\added[id=JJ]{\citep{Ulrich2011a, Batsleer2015}}.  \added[id=JJ]{This
	discarding of fish in excess of quota hampers the ability to limit
	fishing mortality to within sustainable limits \citep{Alverson1994,
	Crowder1998, Rijnsdorp2007}} \deleted[id=PD]{; reducing
discarding is crucial} to ensure biological and
economic sustainability of fisheries\deleted[id=JJ]{ and implementation of an
	ecosystem approach to fisheries}\replaced[id=PD]{and}{. As such} there
is increasing interest in technical solutions such as gear and spatial closures
as ways of \replaced[id=PD]{reducing unwanted catch}{avoiding
	discard\added[id=JJ]{ing of fish}}\citep{Kennelly2002,
		Catchpole2008, Bellido2011}.  \\

@@

Using our model we simulate \replaced[id=PD]{20}{40} years of exploitation of
the fish populations. \replaced[id=PD]{We}{ and} use the
results\deleted[id=PD]{ from the fishing model:}

@@

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trends}
	\caption{Comparison of closure scenarios - F trends}
	\label{fig:3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/Overview_plot_highPop}
	\caption{Comparison of closure scenarios}
	\label{fig:4}
\end{figure}

>>>>

\replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} a variety 
of spatially and temporally heterogeneous fish populations, using
species-unselective gear that can result in unintended, unwanted catch of low
quota or protected species. Reducing these unwanted catches is crucial for
biological and economic sustainability of `mixed fisheries' and implementation
of an ecosystem approach to fishing. \\

\replaced[id = PD]{If fisheries are to avoid unwanted catch}{To implement
	effective spatial measures to reduce discards} a good understanding of
spatiotemporal fishery dynamics is required. However, traditional scientific
advice is limited by a lack of highly resolved knowledge of population
distributions, movement and how fishers interact with different fish
populations. This reflects the fact that data on fish location at high temporal
and spatial resolutions is expensive and difficult to collect. Proxies inferred
from either scientific surveys or commercial catch data are often used to model
distributions, often with data at limited spatial and temporal resolution. \\

To understand how data resolution impacts inference on mixed fisheries
interactions, we develop a highly resolved spatiotemporal simulation model
incorporating: i) delay-difference population dynamics, ii) population movement
using Gaussian Random Fields to simulate patchy, heterogeneously distributed
populations, and iii) fishery dynamics for multiple fleet characteristics based
on species targeting via a mix of correlated random walk movement (for
exploration) and learned behaviour (for exploitation) phases of the fisheries.
\\

We simulate 50 years of fishing and use the results from the fisheries catch to
draw inference on the underlying population structures. We compare this
inference to i) a simulated fixed-site sampling design commonly used for
fisheries monitoring purposes, and ii) the true underlying population
structures input to the simulation, to establish the potential and limitations
of fishery-dependent data - an inherently biased sampling method due to
fisher's targeting- to provide a robust picture of spatiotemporal
distributions. Finally, we simulate an area closure based on areas defined from
commercial the known ("real-population") distribution, commercial catch data
and survey data at different temporal and spatial resolutions and assess their
effectiveness on reducing catches of a fish population. \\

@@

Fishers exploit a variety of fish populations that are heterogeneously
distributed in space and time with varying knowledge of species distributions
using species-unselective fishing gear. \added[id=PD]{In doing so} fisheries
\deleted[id=PD]{that} catch an assemblage of species
\added[id=PD]{and}\deleted{, known as mixed fisheries} \replaced[id=JJ]{may}{,
	when managed by single-species quotas can end up}
discard\deleted[id=JJ]{ing} overquota catch \added[id=JJ]{when managed by
	single species quotas,} leading to overexploitation of fish populations
\added[id=JJ]{\citep{Ulrich2011a, Batsleer2015}}.  \added[id=JJ]{This
	discarding of fish in excess of quota hampers the ability to limit
	fishing mortality to within sustainable limits \citep{Alverson1994,
		Crowder1998, Rijnsdorp2007}} \deleted[id=PD]{; reducing
	discarding is crucial}and ensure biological and economic sustainability
of fisheries\deleted[id=JJ]{ and implementation of an ecosystem approach to
	fisheries}. As such, there is increasing interest
in technical solutions such as gear and spatial closures as ways of
\replaced[id=PD]{reducing unwanted catch}{avoiding discard\added[id=JJ]{ing of
		fish}}\citep{Kennelly2002, Catchpole2008, Bellido2011}.  \\

@@

Using our model we simulate \replaced[id=PD]{50}{40} years of exploitation of
the fish populations. \replaced[id=PD]{We}{ and} use the
results\deleted[id=PD]{ from the fishing model:}

@@

NOTE: THIS IS EXPLORE-EXPLOIT STRATEGY VIZ. BAILEY ET AL POSEIDON MODEL.

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
	\caption{Comparison of closure scenarios - F trends}
	\label{fig:3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width =\linewidth]{../analysis/Overview_plot_highPopRev}
	\caption{Comparison of closure scenarios}
	\label{fig:4}
\end{figure}
